An efficient acyclic contact planner for legged robots

### 2017-01-18 main.tex
Nouvel abstract Main.tex change pour pb de compilation.
Move Section about heuristics to Appendix
replaced contact feasible with contact reachable to match with reachability confition
updated overview
merging appendices
florent s comment
andrea s comment + reviewers

% Another method to track changes
% Examples of usage:
% - This is \added[id=per,remark={we need this}]{new} text.
% - This is \deleted[id=per,remark=obsolete]{unnecessary}text.
% - This is \replaced[id=per]{nice}{bad} text.
% To print the list of change use: \listofchanges
\usepackage{changes}	% use this for the working version
%\usepackage[final]{changes} % use this for the final version
\definechangesauthor[name={Andrea Del Prete}, color=orange]{adp}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
\usepackage{glossaries}

@@

\makeglossaries
\input{body/glossary}

@@

\title{An efficient acyclic contact planner for multiped robots}

\author{Steve Tonneau\affilnum{1}, Andrea Del Prete\affilnum{1}, Julien Pettr\'e\affilnum{2}, Chonhyon Park\affilnum{3}, Dinesh Manocha\affilnum{3}, Nicolas Mansard\affilnum{1}}
 %~ Franck Multon\affilnum{3},
\affiliation{\affilnum{1}LAAS-CNRS / Universit\'e Paul Sabatier, Toulouse, France\\
\affilnum{2}Inria, Rennes, France\\
\affilnum{3}UNC, Chapel Hill, USA  } % \\
%~ \affilnum{3}Universit\'e Rennes 2, France}

@@

\section{Introduction}
\input{body/intro}
\input{body/overview}
\input{body/rbprm}
\input{body/contact}
\input{body/equilibrium}
\input{body/efort}
\input{body/results}
\input{body/conclusion}
\section*{Acknowledgements}
This research is supported by Euroc (project under FP7 Grant Agreement  608849);  Entracte (ANR  grant  agreement  13-CORD-002-01);
the ARO Contract W911NF-14-1-0437; and the NSF award 1305286. %, and a grant from Boeing.
%~ \theendnotes

\glsaddall
\printglossaries
\bibliographystyle{SageH}
\bibliography{biblio}
\appendix
\input{body/appendix_roms}
\input{body/appendix_algo}
\input{body/appendix_hpp}
\end{document}

>>>>

% Another method to track changes
% Examples of usage:
% - This is \added[id=per,remark={we need this}]{new} text.
% - This is \deleted[id=per,remark=obsolete]{unnecessary}text.
% - This is \replaced[id=per]{nice}{bad} text.
% To print the list of change use: \listofchanges
\usepackage{changes}	% use this for the working version
%\usepackage[final]{changes} % use this for the final version
\definechangesauthor[name={Andrea Del Prete}, color=orange]{adp}
\newcommand{\deladp}[1]{\deleted[id=adp]{#1}}
\newcommand{\addadp}[1]{\added[id=adp]{#1}}
\newcommand{\repadp}[2]{\replaced[id=adp]{#1}{#2}}
\definechangesauthor[name={Steve Tonneau}, color=blue]{st}
\newcommand{\delst}[1]{\deleted[id=st]{#1}}
\newcommand{\addst}[1]{\added[id=st]{#1}}
\newcommand{\repst}[2]{\replaced[id=st]{#1}{#2}}
\newcommand{\gls}[1]{\textit{#1}}
\newcommand{\glslink}[2]{{#2}}

%~ \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red,draft]{hyperref}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
%~ \usepackage{glossaries}

@@

%~ \makeglossaries
%~ \input{body/glossary}

@@

\title{An efficient acyclic contact planner for legged robots}

\author{Steve Tonneau\affilnum{1}, Andrea Del Prete\affilnum{1}, Julien Pettr\'e\affilnum{2}, Chonhyon Park\affilnum{3}, Dinesh Manocha\affilnum{3}, Nicolas Mansard\affilnum{1}}
 %~ Franck Multon\affilnum{3},
\affiliation{\affilnum{1}LAAS-CNRS / Universit\'e de Toulouse, France\\
\affilnum{2}Inria, Rennes, France\\
\affilnum{3}UNC, Chapel Hill, USA  } % \\
%~ \affilnum{3}Universit\'e Rennes 2, France}

@@

\section{Introduction}
\input{body/intro}
\input{body/overview}
\input{body/rbprm}
\input{body/contact}
\input{body/results}
\input{body/conclusion}
\section*{Acknowledgements}
This research is supported by Euroc (project under FP7 Grant Agreement  608849);  Entracte (ANR  grant  agreement  13-CORD-002-01);
the ARO Contract W911NF-14-1-0437; and the NSF award 1305286. %, and a grant from Boeing.
%~ \theendnotes

%~ \appendix
%~ \section*{Appendix}

%~ \glsaddall
%~ \printglossaries
\bibliographystyle{SageH}
\bibliography{biblio}
\appendix
\input{body/equilibrium}
\input{body/efort}
\input{body/appendix_roms}
\input{body/appendix_algo}
\input{body/appendix_hpp}
\end{document}
